---
title: "LCGA 7 timeslots"
author: "Chaochen Wang"
date: "Created at 28 July 2018, Updated at `r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
    nature:
      highlightLines: true
editor_options: 
  chunk_output_type: console
---

# Response to carb intake and time slot definition


- In this analysis, within each **time slot** of the day carbohydrates intake was defined as: 
    - not eating; 
    - eating and carbohydrates contributed less than 50% of energy;
    - eating and carbohydrates contributed higher or equal to 50% of energy.
    
- Time slots are defined as: 
    - **Breakfast:** 6 am to 9 am; 
    - **Morning snack:** 9 am to 12 noon; 
    - **Lunch:** 12 noon to 2 pm; 
    - **Afternoon snack:** 2 pm to 5 pm; 
    - **Dinner:** 5 pm to 8 pm; 
    - **Before bedtime snack:** 8 pm to 10 pm; 
    - **Midnight food:** 10pm to 6 am;
    



# Model comparison and selection

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(RColorBrewer)
library(plyr)
library(tidyverse)
library(dplyr)
library(epiDisplay)
library(scales)
library(readr)
rm(list=ls(all=TRUE))
# load("~/Documents/LSHTMproject/Rcode/day4LCA1_6.Rdata")

library(kableExtra)
dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/ndns_LGCA_slots.csv", header = T)
names(dt) <- c("N of classes", "N of free parameters","log-likelihood",  "AIC", "BIC", "aBIC", "Entropy")
# dt[1,8] <- "--"
# dt[2,8] <- "< 0.0001"
# dt[3,8] <- "< 0.0001"
kable(dt, digits = 4, row.names = FALSE, align = "c",
              format = "html", caption = "Latent class growth analysis class selection. (All data, n = 6155, 24483 data points)") %>%
 kable_styling(font_size = 16, 
        bootstrap_options = c("striped", "hover", "condensed"),
        position = "center", full_width = FALSE) %>% 
  # row_spec(3, bold = T, color = "white", background = "#D7261E") %>% 
  footnote(general = "Abbreviation: N, number; AIC, Akaike information criterion; BIC, Bayesian information criterion; aBIC, adjusted BIC; Entropy, a pseudo-r-squared index.")
```


# LCGA in four days of Survey (2 classes)


```{r echo=FALSE, fig.height=6, fig.width=15, message=FALSE, warning=FALSE, cache=TRUE}
library(readr)
Slots_LGCA_2CLASS <- read_table2("/home/wangcc-me/Documents/LSHTMproject/results/Timeslots/LGCA/NDNSslot_LGCA_2CLASS.txt", 
    col_names = FALSE)


Slots_LGCA_2CLASS[, 1:32] <- sapply(Slots_LGCA_2CLASS[, 1:32], as.numeric)
names(Slots_LGCA_2CLASS) <- c(
  "H6_9_X",  "H9_12_X",
  "H12_14_X",  "H14_17_X",
  "H17_20_X",  "H20_22_X",
  "H22_6_X",  
  "H6_9_Y",  "H9_12_Y",
  "H12_14_Y",  "H14_17_Y",
  "H17_20_Y",  "H20_22_Y",
  "H22_6_Y",  
  "H6_9_X_X",  "H9_12_X_X",
  "H12_14_X_X",  "H14_17_X_X",
  "H17_20_X_X",  "H20_22_X_X",
  "H22_6_X_X",  
  "H6_9_Y_Y",  "H9_12_Y_Y",
  "H12_14_Y_Y",  "H14_17_Y_Y",
  "H17_20_Y_Y",  "H20_22_Y_Y",
  "H22_6_Y_Y",  
  "ID",
  "CPROB1",  "CPROB2",
  #"CPROB3",  #"CPROB4", 
  "C")

Slots_LGCA_2CLASS[Slots_LGCA_2CLASS == "*"] <- NA
ppd1 <- Slots_LGCA_2CLASS %>% 
  group_by(C) %>% 
  summarise(d1H6_9_0 = sum(H6_9_X == 0, na.rm = T)/length(H6_9_X), 
            d1H6_9_1 = sum(H6_9_X == 1, na.rm = T)/length(H6_9_X), 
            d1H6_9_2 = sum(H6_9_X == 2, na.rm = T)/length(H6_9_X),
            d1H9_12_0 = sum(H9_12_X == 0, na.rm = T)/length(H9_12_X),
            d1H9_12_1 = sum(H9_12_X == 1, na.rm = T)/length(H9_12_X), 
            d1H9_12_2 = sum(H9_12_X == 2, na.rm = T)/length(H9_12_X),
            d1H12_14_0 = sum(H12_14_X == 0, na.rm = T)/length(H12_14_X),
            d1H12_14_1 = sum(H12_14_X == 1, na.rm = T)/length(H12_14_X), 
            d1H12_14_2 = sum(H12_14_X == 2, na.rm = T)/length(H12_14_X),
            d1H14_17_0 = sum(H14_17_X == 0, na.rm = T)/length(H14_17_X),
            d1H14_17_1 = sum(H14_17_X == 1, na.rm = T)/length(H14_17_X), 
            d1H14_17_2 = sum(H14_17_X == 2, na.rm = T)/length(H14_17_X),
            d1H17_20_0 = sum(H17_20_X == 0, na.rm = T)/length(H17_20_X),
            d1H17_20_1 = sum(H17_20_X == 1, na.rm = T)/length(H17_20_X), 
            d1H17_20_2 = sum(H17_20_X == 2, na.rm = T)/length(H17_20_X),
            d1H20_22_0 = sum(H20_22_X == 0, na.rm = T)/length(H20_22_X),
            d1H20_22_1 = sum(H20_22_X == 1, na.rm = T)/length(H20_22_X), 
            d1H20_22_2 = sum(H20_22_X == 2, na.rm = T)/length(H20_22_X),
            d1H22_6_0 = sum(H22_6_X == 0, na.rm = T)/length(H22_6_X),
            d1H22_6_1 = sum(H22_6_X == 1, na.rm = T)/length(H22_6_X), 
            d1H22_6_2 = sum(H22_6_X == 2, na.rm = T)/length(H22_6_X)
            )


ppd2 <- Slots_LGCA_2CLASS %>% 
  group_by(C) %>% 
  summarise(d2H6_9_0 = sum(H6_9_Y == 0, na.rm = T)/length(H6_9_Y), 
            d2H6_9_1 = sum(H6_9_Y == 1, na.rm = T)/length(H6_9_Y), 
            d2H6_9_2 = sum(H6_9_Y == 2, na.rm = T)/length(H6_9_Y),
            d2H9_12_0 = sum(H9_12_Y == 0, na.rm = T)/length(H9_12_Y),
            d2H9_12_1 = sum(H9_12_Y == 1, na.rm = T)/length(H9_12_Y), 
            d2H9_12_2 = sum(H9_12_Y == 2, na.rm = T)/length(H9_12_Y),
            d2H12_14_0 = sum(H12_14_Y == 0, na.rm = T)/length(H12_14_Y),
            d2H12_14_1 = sum(H12_14_Y == 1, na.rm = T)/length(H12_14_Y), 
            d2H12_14_2 = sum(H12_14_Y == 2, na.rm = T)/length(H12_14_Y),
            d2H14_17_0 = sum(H14_17_Y == 0, na.rm = T)/length(H14_17_Y),
            d2H14_17_1 = sum(H14_17_Y == 1, na.rm = T)/length(H14_17_Y), 
            d2H14_17_2 = sum(H14_17_Y == 2, na.rm = T)/length(H14_17_Y),
            d2H17_20_0 = sum(H17_20_Y == 0, na.rm = T)/length(H17_20_Y),
            d2H17_20_1 = sum(H17_20_Y == 1, na.rm = T)/length(H17_20_Y), 
            d2H17_20_2 = sum(H17_20_Y == 2, na.rm = T)/length(H17_20_Y),
            d2H20_22_0 = sum(H20_22_Y == 0, na.rm = T)/length(H20_22_Y),
            d2H20_22_1 = sum(H20_22_Y == 1, na.rm = T)/length(H20_22_Y), 
            d2H20_22_2 = sum(H20_22_Y == 2, na.rm = T)/length(H20_22_Y),
            d2H22_6_0 = sum(H22_6_Y == 0, na.rm = T)/length(H22_6_Y),
            d2H22_6_1 = sum(H22_6_Y == 1, na.rm = T)/length(H22_6_Y), 
            d2H22_6_2 = sum(H22_6_Y == 2, na.rm = T)/length(H22_6_Y))




ppd3 <- Slots_LGCA_2CLASS %>% 
  group_by(C) %>% 
  summarise(
            d3H6_9_0 = sum(H6_9_X_X == 0.000, na.rm = T)/length(H6_9_X_X), 
            d3H6_9_1 = sum(H6_9_X_X == 1.000, na.rm = T)/length(H6_9_X_X), 
            d3H6_9_2 = sum(H6_9_X_X == 2.000, na.rm = T)/length(H6_9_X_X),
            d3H9_12_0 = sum(H9_12_X_X == 0.000, na.rm = T)/length(H9_12_X_X),
            d3H9_12_1 = sum(H9_12_X_X == 1.000, na.rm = T)/length(H9_12_X_X), 
            d3H9_12_2 = sum(H9_12_X_X == 2.000, na.rm = T)/length(H9_12_X_X),
            d3H12_14_0 = sum(H12_14_X_X == 0.000, na.rm = T)/length(H12_14_X_X),
            d3H12_14_1 = sum(H12_14_X_X == 1.000, na.rm = T)/length(H12_14_X_X), 
            d3H12_14_2 = sum(H12_14_X_X == 2.000, na.rm = T)/length(H12_14_X_X),
            d3H14_17_0 = sum(H14_17_X_X == 0.000, na.rm = T)/length(H14_17_X_X),
            d3H14_17_1 = sum(H14_17_X_X == 1.000, na.rm = T)/length(H14_17_X_X), 
            d3H14_17_2 = sum(H14_17_X_X == 2.000, na.rm = T)/length(H14_17_X_X),
            d3H17_20_0 = sum(H17_20_X_X == 0.000, na.rm = T)/length(H17_20_X_X),
            d3H17_20_1 = sum(H17_20_X_X == 1.000, na.rm = T)/length(H17_20_X_X), 
            d3H17_20_2 = sum(H17_20_X_X == 2.000, na.rm = T)/length(H17_20_X_X),
            d3H20_22_0 = sum(H20_22_X_X == 0.000, na.rm = T)/length(H20_22_X_X),
            d3H20_22_1 = sum(H20_22_X_X == 1.000, na.rm = T)/length(H20_22_X_X), 
            d3H20_22_2 = sum(H20_22_X_X == 2.000, na.rm = T)/length(H20_22_X_X),
            d3H22_6_0 = sum(H22_6_X_X == 0.000, na.rm = T)/length(H22_6_X_X),
            d3H22_6_1 = sum(H22_6_X_X == 1.000, na.rm = T)/length(H22_6_X_X), 
            d3H22_6_2 = sum(H22_6_X_X == 2.000, na.rm = T)/length(H22_6_X_X))


ppd4 <- Slots_LGCA_2CLASS %>% 
  group_by(C) %>% 
  summarise(d4H6_9_0 = sum(H6_9_Y_Y == 0.000, na.rm = T)/length(H6_9_Y_Y), 
            d4H6_9_1 = sum(H6_9_Y_Y == 1.000, na.rm = T)/length(H6_9_Y_Y), 
            d4H6_9_2 = sum(H6_9_Y_Y == 2.000, na.rm = T)/length(H6_9_Y_Y),
            d4H9_12_0 = sum(H9_12_Y_Y == 0.000, na.rm = T)/length(H9_12_Y_Y),
            d4H9_12_1 = sum(H9_12_Y_Y == 1.000, na.rm = T)/length(H9_12_Y_Y), 
            d4H9_12_2 = sum(H9_12_Y_Y == 2.000, na.rm = T)/length(H9_12_Y_Y),
            d4H12_14_0 = sum(H12_14_Y_Y == 0.000, na.rm = T)/length(H12_14_Y_Y),
            d4H12_14_1 = sum(H12_14_Y_Y == 1.000, na.rm = T)/length(H12_14_Y_Y), 
            d4H12_14_2 = sum(H12_14_Y_Y == 2.000, na.rm = T)/length(H12_14_Y_Y),
            d4H14_17_0 = sum(H14_17_Y_Y == 0.000, na.rm = T)/length(H14_17_Y_Y),
            d4H14_17_1 = sum(H14_17_Y_Y == 1.000, na.rm = T)/length(H14_17_Y_Y), 
            d4H14_17_2 = sum(H14_17_Y_Y == 2.000, na.rm = T)/length(H14_17_Y_Y),
            d4H17_20_0 = sum(H17_20_Y_Y == 0.000, na.rm = T)/length(H17_20_Y_Y),
            d4H17_20_1 = sum(H17_20_Y_Y == 1.000, na.rm = T)/length(H17_20_Y_Y), 
            d4H17_20_2 = sum(H17_20_Y_Y == 2.000, na.rm = T)/length(H17_20_Y_Y),
            d4H20_22_0 = sum(H20_22_Y_Y == 0.000, na.rm = T)/length(H20_22_Y_Y),
            d4H20_22_1 = sum(H20_22_Y_Y == 1.000, na.rm = T)/length(H20_22_Y_Y), 
            d4H20_22_2 = sum(H20_22_Y_Y == 2.000, na.rm = T)/length(H20_22_Y_Y),
            d4H22_6_0 = sum(H22_6_Y_Y == 0.000, na.rm = T)/length(H22_6_Y_Y),
            d4H22_6_1 = sum(H22_6_Y_Y == 1.000, na.rm = T)/length(H22_6_Y_Y), 
            d4H22_6_2 = sum(H22_6_Y_Y == 2.000, na.rm = T)/length(H22_6_Y_Y))



ppd1_long <- ppd1 %>% 
  gather(DHour, Prob, -C) %>% 
  separate(DHour, into = c("DHourN", "HourEnd", "Carbo"), sep = "_(?=[:digit:])") 
ppd2_long <- ppd2 %>% 
  gather(DHour, Prob, -C) %>% 
  separate(DHour, into = c("DHourN", "HourEnd","Carbo"), sep = "_(?=[:digit:])") 
ppd3_long <- ppd3 %>% 
  gather(DHour, Prob, -C) %>% 
  separate(DHour, into = c("DHourN", "HourEnd", "Carbo"), sep = "_(?=[:digit:])") 
ppd4_long <- ppd4 %>% 
  gather(DHour, Prob, -C) %>% 
  separate(DHour, into = c("DHourN", "HourEnd", "Carbo"), sep = "_(?=[:digit:])") 


pp <- bind_rows(ppd1_long, ppd2_long, ppd3_long, ppd4_long)


pp$DHourN <- factor(pp$DHourN, 
                        levels = c("d1H6",  "d1H9",
                                   "d1H12",  "d1H14",
                                   "d1H17",  "d1H20",
                                   "d1H22",  
                                   "d2H6",    "d2H9",
                                   "d2H12",  "d2H14",
                                   "d2H17",  "d2H20",
                                   "d2H22",  
                                   "d3H6",    "d3H9",
                                   "d3H12",    "d3H14",
                                   "d3H17",    "d3H20",
                                   "d3H22",  
                                   "d4H6",    "d4H9",
                                   "d4H12",   "d4H14",
                                   "d4H17",   "d4H20",
                                   "d4H22"))







library(ggthemr)
ggthemr("fresh", layout = "scientific")
library(ggplot2)


ggplot(pp[pp$C == 1, ], aes(y = Prob, x=DHourN, group = Carbo, color = Carbo)) + 
  geom_point(size = 2) + 
  geom_line(size = 1) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(face="bold", size = 14), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15),
        legend.position = "bottom",
        legend.direction = "horizontal"
  ) + 
  labs(title = "Class 1: 43.9%", x = "Time slots of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Not eating\nany food", "< 50%", ">= 50%")) + 
  ylim(c(0,1)) + 
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  annotate("rect", xmin = "d1H6", xmax = "d2H6", ymin = 0, ymax = 1.00, 
            alpha = 0.2, fill = "pink") + 
  annotate("rect", xmin = "d2H6", xmax = "d3H6", ymin = 0, ymax = 1.00, 
             alpha = 0.18, fill = "turquoise") + 
  annotate("rect", xmin = "d3H6", xmax = "d4H6", ymin = 0, ymax = 1.00, 
            alpha = 0.2, fill = "pink") + 
  annotate("rect", xmin = "d4H6", xmax = "d4H22", ymin = 0, ymax = 1.00, 
             alpha = 0.18, fill = "turquoise") + 
  annotate("text", x = "d1H12", y = 0.9,
            label = "Day 1", size = 7) +
  annotate("text", x = "d2H12", y = 0.9,
            label = "Day 2", size = 7) + 
  annotate("text", x = "d3H12", y = 0.9,
            label = "Day 3", size = 7) +
  annotate("text", x = "d4H12", y = 0.9,
            label = "Day 4", size = 7) + 
  scale_x_discrete(labels=c(        "d1H6" = "Breakfast",    "d1H9" = "Morning snack",
                                   "d1H12" = "Lunch",  "d1H14" = "Afternoon snack",
                                   "d1H17" = "Dinner",  "d1H20" = "Before bedtime snack",
                                   "d1H22" = "Midnight food",  
                                   "d2H6" = "Breakfast",    "d2H9" = "Morning snack",
                                   "d2H12" = "Lunch",  "d2H14" = "Afternoon snack",
                                   "d2H17" = "Dinner",  "d2H20" = "Before bedtime snack",
                                   "d2H22" = "Midnight food",
                                   "d3H6" = "Breakfast",    "d3H9" = "Morning snack",
                                   "d3H12" = "Lunch",  "d3H14" = "Afternoon snack",
                                   "d3H17" = "Dinner",  "d3H20" = "Before bedtime snack",
                                   "d3H22" = "Midnight food",
                                  "d4H6" = "Breakfast",    "d4H9" = "Morning snack",
                                   "d4H12" = "Lunch",  "d4H14" = "Afternoon snack",
                                   "d4H17" = "Dinner",  "d4H20" = "Before bedtime snack",
                                   "d4H22" = "Midnight food"
  ))






ggplot(pp[pp$C == 2, ], aes(y = Prob, x=DHourN, group = Carbo, color = Carbo)) + 
  geom_point(size = 2) + 
  geom_line(size = 1) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(face="bold", size = 14), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15), 
        legend.position = "bottom",
        legend.direction = "horizontal"
  ) + 
  labs(title = "Class 2: 56.1%", x = "Time slots of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Not eating\nany food", "< 50%", ">= 50%")) + 
  ylim(c(0,1)) + 
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  annotate("rect", xmin = "d1H6", xmax = "d2H6", ymin = 0, ymax = 1.00, 
            alpha = 0.2, fill = "pink") + 
  annotate("rect", xmin = "d2H6", xmax = "d3H6", ymin = 0, ymax = 1.00, 
             alpha = 0.18, fill = "turquoise") + 
  annotate("rect", xmin = "d3H6", xmax = "d4H6", ymin = 0, ymax = 1.00, 
            alpha = 0.2, fill = "pink") + 
  annotate("rect", xmin = "d4H6", xmax = "d4H22", ymin = 0, ymax = 1.00, 
             alpha = 0.18, fill = "turquoise") + 
  annotate("text", x = "d1H12", y = 0.9,
            label = "Day 1", size = 7) +
  annotate("text", x = "d2H12", y = 0.9,
            label = "Day 2", size = 7) + 
  annotate("text", x = "d3H12", y = 0.9,
            label = "Day 3", size = 7) +
  annotate("text", x = "d4H12", y = 0.9,
            label = "Day 4", size = 7) + 
  scale_x_discrete(labels=c(        "d1H6" = "Breakfast",    "d1H9" = "Morning snack",
                                   "d1H12" = "Lunch",  "d1H14" = "Afternoon snack",
                                   "d1H17" = "Dinner",  "d1H20" = "Before bedtime snack",
                                   "d1H22" = "Midnight food",  
                                   "d2H6" = "Breakfast",    "d2H9" = "Morning snack",
                                   "d2H12" = "Lunch",  "d2H14" = "Afternoon snack",
                                   "d2H17" = "Dinner",  "d2H20" = "Before bedtime snack",
                                   "d2H22" = "Midnight food",
                                   "d3H6" = "Breakfast",    "d3H9" = "Morning snack",
                                   "d3H12" = "Lunch",  "d3H14" = "Afternoon snack",
                                   "d3H17" = "Dinner",  "d3H20" = "Before bedtime snack",
                                   "d3H22" = "Midnight food",
                                  "d4H6" = "Breakfast",    "d4H9" = "Morning snack",
                                   "d4H12" = "Lunch",  "d4H14" = "Afternoon snack",
                                   "d4H17" = "Dinner",  "d4H20" = "Before bedtime snack",
                                   "d4H22" = "Midnight food"))


# ggplot(pp[pp$C == 3, ], aes(y = Prob, x=DHourN, group = Carbo, color = Carbo)) +
#   geom_point(size = 2) + 
#   geom_line(size = 1) + 
#   theme(axis.title = element_text(size = 18), 
#         axis.text = element_text(size = 10), 
#         axis.line = element_line(colour = "black"), 
#         panel.border = element_blank(), 
#         panel.background = element_blank(), 
#         legend.text = element_text(size = 15), 
#         legend.title = element_text(size = 15) 
#         # legend.position = "bottom", 
#         # legend.direction = "horizontal"
#   ) + 
#   labs(title = "Class 3", x = "Time slots of the day", y = "Probability",
#        color = "Carbohydrate\nintake") + 
#   scale_color_discrete(labels = c("Not eating\nany food", "< 50%", ">= 50%")) + 
#   ylim(c(0,1)) + 
#   theme(axis.text.x = element_text(angle = 90, hjust = 1))




# ggplot(pp[pp$C == 4, ], aes(y = Prob, x=DHourN, group = Carbo, color = Carbo)) +
#   geom_point(size = 2) + 
#   geom_line(size = 1) + 
#   theme(axis.title = element_text(size = 18), 
#         axis.text = element_text(size = 10), 
#         axis.line = element_line(colour = "black"), 
#         panel.border = element_blank(), 
#         panel.background = element_blank(), 
#         legend.text = element_text(size = 15), 
#         legend.title = element_text(size = 15) 
#         # legend.position = "bottom", 
#         # legend.direction = "horizontal"
#   ) + 
#   labs(title = "Class 3", x = "Time slots of the day", y = "Probability",
#        color = "Carbohydrate\nintake") + 
#   scale_color_discrete(labels = c("Not eating\nany food", "< 50%", ">= 50%")) + 
#   ylim(c(0,1)) + 
#   theme(axis.text.x = element_text(angle = 90, hjust = 1))
```



# LCGA in four days of Survey (3 classes)


```{r echo=FALSE, fig.height=6, fig.width=15, message=FALSE, warning=FALSE, cache=TRUE}
library(readr)
Slots_LGCA_3CLASS <- read_table2("/home/wangcc-me/Documents/LSHTMproject/results/Timeslots/LGCA/NDNSslot_LGCA_3CLASS.txt", 
    col_names = FALSE)


Slots_LGCA_3CLASS[, 1:32] <- sapply(Slots_LGCA_3CLASS[, 1:32], as.numeric)
names(Slots_LGCA_3CLASS) <- c(
  "H6_9_X",  "H9_12_X",
  "H12_14_X",  "H14_17_X",
  "H17_20_X",  "H20_22_X",
  "H22_6_X",  
  "H6_9_Y",  "H9_12_Y",
  "H12_14_Y",  "H14_17_Y",
  "H17_20_Y",  "H20_22_Y",
  "H22_6_Y",  
  "H6_9_X_X",  "H9_12_X_X",
  "H12_14_X_X",  "H14_17_X_X",
  "H17_20_X_X",  "H20_22_X_X",
  "H22_6_X_X",  
  "H6_9_Y_Y",  "H9_12_Y_Y",
  "H12_14_Y_Y",  "H14_17_Y_Y",
  "H17_20_Y_Y",  "H20_22_Y_Y",
  "H22_6_Y_Y",  
  "ID",
  "CPROB1",  "CPROB2",
  "CPROB3",  #"CPROB4", 
  "C")

Slots_LGCA_3CLASS[Slots_LGCA_3CLASS == "*"] <- NA
ppd1 <- Slots_LGCA_3CLASS %>% 
  group_by(C) %>% 
  summarise(d1H6_9_0 = sum(H6_9_X == 0, na.rm = T)/length(H6_9_X), 
            d1H6_9_1 = sum(H6_9_X == 1, na.rm = T)/length(H6_9_X), 
            d1H6_9_2 = sum(H6_9_X == 2, na.rm = T)/length(H6_9_X),
            d1H9_12_0 = sum(H9_12_X == 0, na.rm = T)/length(H9_12_X),
            d1H9_12_1 = sum(H9_12_X == 1, na.rm = T)/length(H9_12_X), 
            d1H9_12_2 = sum(H9_12_X == 2, na.rm = T)/length(H9_12_X),
            d1H12_14_0 = sum(H12_14_X == 0, na.rm = T)/length(H12_14_X),
            d1H12_14_1 = sum(H12_14_X == 1, na.rm = T)/length(H12_14_X), 
            d1H12_14_2 = sum(H12_14_X == 2, na.rm = T)/length(H12_14_X),
            d1H14_17_0 = sum(H14_17_X == 0, na.rm = T)/length(H14_17_X),
            d1H14_17_1 = sum(H14_17_X == 1, na.rm = T)/length(H14_17_X), 
            d1H14_17_2 = sum(H14_17_X == 2, na.rm = T)/length(H14_17_X),
            d1H17_20_0 = sum(H17_20_X == 0, na.rm = T)/length(H17_20_X),
            d1H17_20_1 = sum(H17_20_X == 1, na.rm = T)/length(H17_20_X), 
            d1H17_20_2 = sum(H17_20_X == 2, na.rm = T)/length(H17_20_X),
            d1H20_22_0 = sum(H20_22_X == 0, na.rm = T)/length(H20_22_X),
            d1H20_22_1 = sum(H20_22_X == 1, na.rm = T)/length(H20_22_X), 
            d1H20_22_2 = sum(H20_22_X == 2, na.rm = T)/length(H20_22_X),
            d1H22_6_0 = sum(H22_6_X == 0, na.rm = T)/length(H22_6_X),
            d1H22_6_1 = sum(H22_6_X == 1, na.rm = T)/length(H22_6_X), 
            d1H22_6_2 = sum(H22_6_X == 2, na.rm = T)/length(H22_6_X)
            )


ppd2 <- Slots_LGCA_3CLASS %>% 
  group_by(C) %>% 
  summarise(d2H6_9_0 = sum(H6_9_Y == 0, na.rm = T)/length(H6_9_Y), 
            d2H6_9_1 = sum(H6_9_Y == 1, na.rm = T)/length(H6_9_Y), 
            d2H6_9_2 = sum(H6_9_Y == 2, na.rm = T)/length(H6_9_Y),
            d2H9_12_0 = sum(H9_12_Y == 0, na.rm = T)/length(H9_12_Y),
            d2H9_12_1 = sum(H9_12_Y == 1, na.rm = T)/length(H9_12_Y), 
            d2H9_12_2 = sum(H9_12_Y == 2, na.rm = T)/length(H9_12_Y),
            d2H12_14_0 = sum(H12_14_Y == 0, na.rm = T)/length(H12_14_Y),
            d2H12_14_1 = sum(H12_14_Y == 1, na.rm = T)/length(H12_14_Y), 
            d2H12_14_2 = sum(H12_14_Y == 2, na.rm = T)/length(H12_14_Y),
            d2H14_17_0 = sum(H14_17_Y == 0, na.rm = T)/length(H14_17_Y),
            d2H14_17_1 = sum(H14_17_Y == 1, na.rm = T)/length(H14_17_Y), 
            d2H14_17_2 = sum(H14_17_Y == 2, na.rm = T)/length(H14_17_Y),
            d2H17_20_0 = sum(H17_20_Y == 0, na.rm = T)/length(H17_20_Y),
            d2H17_20_1 = sum(H17_20_Y == 1, na.rm = T)/length(H17_20_Y), 
            d2H17_20_2 = sum(H17_20_Y == 2, na.rm = T)/length(H17_20_Y),
            d2H20_22_0 = sum(H20_22_Y == 0, na.rm = T)/length(H20_22_Y),
            d2H20_22_1 = sum(H20_22_Y == 1, na.rm = T)/length(H20_22_Y), 
            d2H20_22_2 = sum(H20_22_Y == 2, na.rm = T)/length(H20_22_Y),
            d2H22_6_0 = sum(H22_6_Y == 0, na.rm = T)/length(H22_6_Y),
            d2H22_6_1 = sum(H22_6_Y == 1, na.rm = T)/length(H22_6_Y), 
            d2H22_6_2 = sum(H22_6_Y == 2, na.rm = T)/length(H22_6_Y))




ppd3 <- Slots_LGCA_3CLASS %>% 
  group_by(C) %>% 
  summarise(
            d3H6_9_0 = sum(H6_9_X_X == 0.000, na.rm = T)/length(H6_9_X_X), 
            d3H6_9_1 = sum(H6_9_X_X == 1.000, na.rm = T)/length(H6_9_X_X), 
            d3H6_9_2 = sum(H6_9_X_X == 2.000, na.rm = T)/length(H6_9_X_X),
            d3H9_12_0 = sum(H9_12_X_X == 0.000, na.rm = T)/length(H9_12_X_X),
            d3H9_12_1 = sum(H9_12_X_X == 1.000, na.rm = T)/length(H9_12_X_X), 
            d3H9_12_2 = sum(H9_12_X_X == 2.000, na.rm = T)/length(H9_12_X_X),
            d3H12_14_0 = sum(H12_14_X_X == 0.000, na.rm = T)/length(H12_14_X_X),
            d3H12_14_1 = sum(H12_14_X_X == 1.000, na.rm = T)/length(H12_14_X_X), 
            d3H12_14_2 = sum(H12_14_X_X == 2.000, na.rm = T)/length(H12_14_X_X),
            d3H14_17_0 = sum(H14_17_X_X == 0.000, na.rm = T)/length(H14_17_X_X),
            d3H14_17_1 = sum(H14_17_X_X == 1.000, na.rm = T)/length(H14_17_X_X), 
            d3H14_17_2 = sum(H14_17_X_X == 2.000, na.rm = T)/length(H14_17_X_X),
            d3H17_20_0 = sum(H17_20_X_X == 0.000, na.rm = T)/length(H17_20_X_X),
            d3H17_20_1 = sum(H17_20_X_X == 1.000, na.rm = T)/length(H17_20_X_X), 
            d3H17_20_2 = sum(H17_20_X_X == 2.000, na.rm = T)/length(H17_20_X_X),
            d3H20_22_0 = sum(H20_22_X_X == 0.000, na.rm = T)/length(H20_22_X_X),
            d3H20_22_1 = sum(H20_22_X_X == 1.000, na.rm = T)/length(H20_22_X_X), 
            d3H20_22_2 = sum(H20_22_X_X == 2.000, na.rm = T)/length(H20_22_X_X),
            d3H22_6_0 = sum(H22_6_X_X == 0.000, na.rm = T)/length(H22_6_X_X),
            d3H22_6_1 = sum(H22_6_X_X == 1.000, na.rm = T)/length(H22_6_X_X), 
            d3H22_6_2 = sum(H22_6_X_X == 2.000, na.rm = T)/length(H22_6_X_X))


ppd4 <- Slots_LGCA_3CLASS %>% 
  group_by(C) %>% 
  summarise(d4H6_9_0 = sum(H6_9_Y_Y == 0.000, na.rm = T)/length(H6_9_Y_Y), 
            d4H6_9_1 = sum(H6_9_Y_Y == 1.000, na.rm = T)/length(H6_9_Y_Y), 
            d4H6_9_2 = sum(H6_9_Y_Y == 2.000, na.rm = T)/length(H6_9_Y_Y),
            d4H9_12_0 = sum(H9_12_Y_Y == 0.000, na.rm = T)/length(H9_12_Y_Y),
            d4H9_12_1 = sum(H9_12_Y_Y == 1.000, na.rm = T)/length(H9_12_Y_Y), 
            d4H9_12_2 = sum(H9_12_Y_Y == 2.000, na.rm = T)/length(H9_12_Y_Y),
            d4H12_14_0 = sum(H12_14_Y_Y == 0.000, na.rm = T)/length(H12_14_Y_Y),
            d4H12_14_1 = sum(H12_14_Y_Y == 1.000, na.rm = T)/length(H12_14_Y_Y), 
            d4H12_14_2 = sum(H12_14_Y_Y == 2.000, na.rm = T)/length(H12_14_Y_Y),
            d4H14_17_0 = sum(H14_17_Y_Y == 0.000, na.rm = T)/length(H14_17_Y_Y),
            d4H14_17_1 = sum(H14_17_Y_Y == 1.000, na.rm = T)/length(H14_17_Y_Y), 
            d4H14_17_2 = sum(H14_17_Y_Y == 2.000, na.rm = T)/length(H14_17_Y_Y),
            d4H17_20_0 = sum(H17_20_Y_Y == 0.000, na.rm = T)/length(H17_20_Y_Y),
            d4H17_20_1 = sum(H17_20_Y_Y == 1.000, na.rm = T)/length(H17_20_Y_Y), 
            d4H17_20_2 = sum(H17_20_Y_Y == 2.000, na.rm = T)/length(H17_20_Y_Y),
            d4H20_22_0 = sum(H20_22_Y_Y == 0.000, na.rm = T)/length(H20_22_Y_Y),
            d4H20_22_1 = sum(H20_22_Y_Y == 1.000, na.rm = T)/length(H20_22_Y_Y), 
            d4H20_22_2 = sum(H20_22_Y_Y == 2.000, na.rm = T)/length(H20_22_Y_Y),
            d4H22_6_0 = sum(H22_6_Y_Y == 0.000, na.rm = T)/length(H22_6_Y_Y),
            d4H22_6_1 = sum(H22_6_Y_Y == 1.000, na.rm = T)/length(H22_6_Y_Y), 
            d4H22_6_2 = sum(H22_6_Y_Y == 2.000, na.rm = T)/length(H22_6_Y_Y))



ppd1_long <- ppd1 %>% 
  gather(DHour, Prob, -C) %>% 
  separate(DHour, into = c("DHourN", "HourEnd", "Carbo"), sep = "_(?=[:digit:])") 
ppd2_long <- ppd2 %>% 
  gather(DHour, Prob, -C) %>% 
  separate(DHour, into = c("DHourN", "HourEnd","Carbo"), sep = "_(?=[:digit:])") 
ppd3_long <- ppd3 %>% 
  gather(DHour, Prob, -C) %>% 
  separate(DHour, into = c("DHourN", "HourEnd", "Carbo"), sep = "_(?=[:digit:])") 
ppd4_long <- ppd4 %>% 
  gather(DHour, Prob, -C) %>% 
  separate(DHour, into = c("DHourN", "HourEnd", "Carbo"), sep = "_(?=[:digit:])") 


pp <- bind_rows(ppd1_long, ppd2_long, ppd3_long, ppd4_long)


pp$DHourN <- factor(pp$DHourN, 
                        levels = c("d1H6",  "d1H9",
                                   "d1H12",  "d1H14",
                                   "d1H17",  "d1H20",
                                   "d1H22",  
                                   "d2H6",    "d2H9",
                                   "d2H12",  "d2H14",
                                   "d2H17",  "d2H20",
                                   "d2H22",  
                                   "d3H6",    "d3H9",
                                   "d3H12",    "d3H14",
                                   "d3H17",    "d3H20",
                                   "d3H22",  
                                   "d4H6",    "d4H9",
                                   "d4H12",   "d4H14",
                                   "d4H17",   "d4H20",
                                   "d4H22"))







library(ggthemr)
ggthemr("fresh", layout = "scientific")
library(ggplot2)


ggplot(pp[pp$C == 1, ], aes(y = Prob, x=DHourN, group = Carbo, color = Carbo)) + 
  geom_point(size = 2) + 
  geom_line(size = 1) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(face="bold", size = 14), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15),
        legend.position = "bottom",
        legend.direction = "horizontal"
  ) + 
  labs(title = "Class 1: 67.2%", x = "Time slots of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Not eating\nany food", "< 50%", ">= 50%")) + 
  ylim(c(0,1)) + 
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  annotate("rect", xmin = "d1H6", xmax = "d2H6", ymin = 0, ymax = 1.00, 
            alpha = 0.2, fill = "pink") + 
  annotate("rect", xmin = "d2H6", xmax = "d3H6", ymin = 0, ymax = 1.00, 
             alpha = 0.18, fill = "turquoise") + 
  annotate("rect", xmin = "d3H6", xmax = "d4H6", ymin = 0, ymax = 1.00, 
            alpha = 0.2, fill = "pink") + 
  annotate("rect", xmin = "d4H6", xmax = "d4H22", ymin = 0, ymax = 1.00, 
             alpha = 0.18, fill = "turquoise") + 
  annotate("text", x = "d1H12", y = 0.9,
            label = "Day 1", size = 7) +
  annotate("text", x = "d2H12", y = 0.9,
            label = "Day 2", size = 7) + 
  annotate("text", x = "d3H12", y = 0.9,
            label = "Day 3", size = 7) +
  annotate("text", x = "d4H12", y = 0.9,
            label = "Day 4", size = 7) + 
   scale_x_discrete(labels=c(        "d1H6" = "Breakfast",    "d1H9" = "Morning snack",
                                   "d1H12" = "Lunch",  "d1H14" = "Afternoon snack",
                                   "d1H17" = "Dinner",  "d1H20" = "Before bedtime snack",
                                   "d1H22" = "Midnight food",  
                                   "d2H6" = "Breakfast",    "d2H9" = "Morning snack",
                                   "d2H12" = "Lunch",  "d2H14" = "Afternoon snack",
                                   "d2H17" = "Dinner",  "d2H20" = "Before bedtime snack",
                                   "d2H22" = "Midnight food",
                                   "d3H6" = "Breakfast",    "d3H9" = "Morning snack",
                                   "d3H12" = "Lunch",  "d3H14" = "Afternoon snack",
                                   "d3H17" = "Dinner",  "d3H20" = "Before bedtime snack",
                                   "d3H22" = "Midnight food",
                                  "d4H6" = "Breakfast",    "d4H9" = "Morning snack",
                                   "d4H12" = "Lunch",  "d4H14" = "Afternoon snack",
                                   "d4H17" = "Dinner",  "d4H20" = "Before bedtime snack",
                                   "d4H22" = "Midnight food"))



ggplot(pp[pp$C == 2, ], aes(y = Prob, x=DHourN, group = Carbo, color = Carbo)) + 
  geom_point(size = 2) + 
  geom_line(size = 1) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(face="bold", size = 14), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15), 
        legend.position = "bottom",
        legend.direction = "horizontal"
  ) + 
  labs(title = "Class 2: 21.9%", x = "Time slots of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Not eating\nany food", "< 50%", ">= 50%")) + 
  ylim(c(0,1)) + 
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  annotate("rect", xmin = "d1H6", xmax = "d2H6", ymin = 0, ymax = 1.00, 
            alpha = 0.2, fill = "pink") + 
  annotate("rect", xmin = "d2H6", xmax = "d3H6", ymin = 0, ymax = 1.00, 
             alpha = 0.18, fill = "turquoise") + 
  annotate("rect", xmin = "d3H6", xmax = "d4H6", ymin = 0, ymax = 1.00, 
            alpha = 0.2, fill = "pink") + 
  annotate("rect", xmin = "d4H6", xmax = "d4H22", ymin = 0, ymax = 1.00, 
             alpha = 0.18, fill = "turquoise") + 
  annotate("text", x = "d1H12", y = 0.9,
            label = "Day 1", size = 7) +
  annotate("text", x = "d2H12", y = 0.9,
            label = "Day 2", size = 7) + 
  annotate("text", x = "d3H12", y = 0.9,
            label = "Day 3", size = 7) +
  annotate("text", x = "d4H12", y = 0.9,
            label = "Day 4", size = 7) + 
 scale_x_discrete(labels=c(        "d1H6" = "Breakfast",    "d1H9" = "Morning snack",
                                   "d1H12" = "Lunch",  "d1H14" = "Afternoon snack",
                                   "d1H17" = "Dinner",  "d1H20" = "Before bedtime snack",
                                   "d1H22" = "Midnight food",  
                                   "d2H6" = "Breakfast",    "d2H9" = "Morning snack",
                                   "d2H12" = "Lunch",  "d2H14" = "Afternoon snack",
                                   "d2H17" = "Dinner",  "d2H20" = "Before bedtime snack",
                                   "d2H22" = "Midnight food",
                                   "d3H6" = "Breakfast",    "d3H9" = "Morning snack",
                                   "d3H12" = "Lunch",  "d3H14" = "Afternoon snack",
                                   "d3H17" = "Dinner",  "d3H20" = "Before bedtime snack",
                                   "d3H22" = "Midnight food",
                                  "d4H6" = "Breakfast",    "d4H9" = "Morning snack",
                                   "d4H12" = "Lunch",  "d4H14" = "Afternoon snack",
                                   "d4H17" = "Dinner",  "d4H20" = "Before bedtime snack",
                                   "d4H22" = "Midnight food"))



ggplot(pp[pp$C == 3, ], aes(y = Prob, x=DHourN, group = Carbo, color = Carbo)) +
  geom_point(size = 2) +
  geom_line(size = 1) +
   theme(axis.title = element_text(size = 18), 
        axis.text = element_text(face="bold", size = 14), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15), 
        legend.position = "bottom",
        legend.direction = "horizontal"
  ) + 
  labs(title = "Class 3: 10.9%", x = "Time slots of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Not eating\nany food", "< 50%", ">= 50%")) + 
  ylim(c(0,1)) + 
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  annotate("rect", xmin = "d1H6", xmax = "d2H6", ymin = 0, ymax = 1.00, 
            alpha = 0.2, fill = "pink") + 
  annotate("rect", xmin = "d2H6", xmax = "d3H6", ymin = 0, ymax = 1.00, 
             alpha = 0.18, fill = "turquoise") + 
  annotate("rect", xmin = "d3H6", xmax = "d4H6", ymin = 0, ymax = 1.00, 
            alpha = 0.2, fill = "pink") + 
  annotate("rect", xmin = "d4H6", xmax = "d4H22", ymin = 0, ymax = 1.00, 
             alpha = 0.18, fill = "turquoise") + 
  annotate("text", x = "d1H12", y = 0.9,
            label = "Day 1", size = 7) +
  annotate("text", x = "d2H12", y = 0.9,
            label = "Day 2", size = 7) + 
  annotate("text", x = "d3H12", y = 0.9,
            label = "Day 3", size = 7) +
  annotate("text", x = "d4H12", y = 0.9,
            label = "Day 4", size = 7) + 
  scale_x_discrete(labels=c(        "d1H6" = "Breakfast",    "d1H9" = "Morning snack",
                                   "d1H12" = "Lunch",  "d1H14" = "Afternoon snack",
                                   "d1H17" = "Dinner",  "d1H20" = "Before bedtime snack",
                                   "d1H22" = "Midnight food",  
                                   "d2H6" = "Breakfast",    "d2H9" = "Morning snack",
                                   "d2H12" = "Lunch",  "d2H14" = "Afternoon snack",
                                   "d2H17" = "Dinner",  "d2H20" = "Before bedtime snack",
                                   "d2H22" = "Midnight food",
                                   "d3H6" = "Breakfast",    "d3H9" = "Morning snack",
                                   "d3H12" = "Lunch",  "d3H14" = "Afternoon snack",
                                   "d3H17" = "Dinner",  "d3H20" = "Before bedtime snack",
                                   "d3H22" = "Midnight food",
                                  "d4H6" = "Breakfast",    "d4H9" = "Morning snack",
                                   "d4H12" = "Lunch",  "d4H14" = "Afternoon snack",
                                   "d4H17" = "Dinner",  "d4H20" = "Before bedtime snack",
                                   "d4H22" = "Midnight food"))




# ggplot(pp[pp$C == 4, ], aes(y = Prob, x=DHourN, group = Carbo, color = Carbo)) +
#   geom_point(size = 2) + 
#   geom_line(size = 1) + 
#   theme(axis.title = element_text(size = 18), 
#         axis.text = element_text(size = 10), 
#         axis.line = element_line(colour = "black"), 
#         panel.border = element_blank(), 
#         panel.background = element_blank(), 
#         legend.text = element_text(size = 15), 
#         legend.title = element_text(size = 15) 
#         # legend.position = "bottom", 
#         # legend.direction = "horizontal"
#   ) + 
#   labs(title = "Class 3", x = "Time slots of the day", y = "Probability",
#        color = "Carbohydrate\nintake") + 
#   scale_color_discrete(labels = c("Not eating\nany food", "< 50%", ">= 50%")) + 
#   ylim(c(0,1)) + 
#   theme(axis.text.x = element_text(angle = 90, hjust = 1))
```