---
title: "NDNS multilevel carb_50, 7 time slots"
author: "Chaochen Wang"
date: "29 July 2018 created, `r Sys.Date()` updated"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
    nature:
      highlightLines: true
editor_options: 
  chunk_output_type: console
---


# Level 1 classes selection


- In this analysis, within each **time slot** of the day carbohydrates intake was defined as: 
    - not eating; 
    - eating and carbohydrates contributed less than 50% of energy;
    - eating and carbohydrates contributed higher or equal to 50% of energy.
    
- Time slots are defined as: 
    - **Breakfast:** 6 am to 9 am; 
    - **Morning snack:** 9 am to 12 noon; 
    - **Lunch:** 12 noon to 2 pm; 
    - **Afternoon snack:** 2 pm to 5 pm; 
    - **Dinner:** 5 pm to 8 pm; 
    - **Before bedtime snack:** 8 pm to 10 pm; 
    - **Midnight food:** 10pm to 6 am;
    

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(RColorBrewer)
library(plyr)
library(epiDisplay)
library(tidyverse)
library(dplyr)

library(scales)
library(readr)
rm(list=ls(all=TRUE))
# load("~/Documents/LSHTMproject/Rcode/day4LCA1_6.Rdata")

library(kableExtra)
dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/Level1_7slots.csv", header = T, colClasses = "character")
names(dt) <- c("N of classes", "N of free parameters","log-likelihood",  "AIC", "BIC", "aBIC", "Entropy", "Lo-Mendel-Rubin LRT")
# dt[1,8] <- "--"
dt[2,8] <- "< 0.0001"
dt[4,8] <- "< 0.0001"
dt[5,8] <- "< 0.0001"
kable(dt, digits = 3, row.names = FALSE, align = "c",
              format = "html", caption = "Level 1 class selection. (All data, n = 6155, 24483 data points)") %>%
 kable_styling(font_size = 16, 
        bootstrap_options = c("striped", "hover", "condensed"),
        position = "center", full_width = FALSE) %>% 
  # row_spec(c(2,3), bold = T, color = "white", background = "#D7261E") %>% 
  footnote(general = "Abbreviation: N, number; AIC, Akaike information criterion; BIC, Bayesian information criterion; aBIC, adjusted BIC; Entropy, a pseudo-r-squared index; Lo-Mendel-Rubin LRT, likelihood ratio test comparing q classes models with q-1 classes models.")
```    




## Fit information for each model (combination of level 1 and level 2 classes)


```{r echo=FALSE}
rm(list=ls(all=TRUE))
# load("~/Documents/LSHTMproject/Rcode/day4LCA1_6.Rdata")

library(kableExtra)
dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/Mixed_7slots.csv", header = T)
names(dt) <- c("Model", "1 class","2 classes",  "3 classes", "4 classes", "5 classes", "6 classes")
dt[is.na(dt)] <- ""
# library(formattable)
dt %>% 
  # mutate(
  #   `2 classes` = cell_spec(`2 classes`, color = ifelse())) %>% 
  kable(escape = F, 
        digits = 3, row.names = FALSE, align = "l",
        format = "html", caption = "Models Specification") %>% 
  add_header_above(c(" ", "Number of level 1 classes" = 6)) %>% 
  group_rows("Fixed effects model", 1, 5) %>%
  group_rows("Random effects model", 6, 20) %>%
  add_indent(c(2:5,7:10,12:15,17:20)) %>% 
  kable_styling(font_size = 16, 
        bootstrap_options = c("striped", "hover", "condensed"),
        position = "center", full_width = FALSE) %>% 
  #row_spec(c(2,3), bold = T, color = "white", background = "#D7261E") %>% 
  footnote(general = "Abbreviation: No, number; BIC, Bayesian information criterion; Entropy, a pseudo-r-squared index; Lo-Mendel-Rubin LRT, likelihood ratio test comparing q classes models with q-1 classes models.")
```






<!-- # (CW = 2) Level 1 latent classes  -->

<!-- ## Visualisation of level 1 latent classes  -->

<!-- ```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE} -->

<!-- CW2CB2 <- read_table2("/home/wangcc-me/Documents/LSHTMproject/results/Timeslots/NDNSslot_CW2CB2.txt", -->
<!--                          col_names = FALSE) -->

<!-- names(CW2CB2) <- c("Breakfast",  -->
<!--                    "Morning.snack", -->
<!--                    "Lunch", -->
<!--                    "Afternoon.snack", -->
<!--                    "Dinner", -->
<!--                    "Before.bedtime.snack", -->
<!--                    "Midnight.food", -->
<!--                       "ID_DAY", -->
<!--                       "AGE", -->
<!--                       "SEX", -->
<!--                       "CPROB1", -->
<!--                       "CPROB2", -->
<!--                       "CPROB3", -->
<!--                       "CPROB4", -->
<!--                       # "CPROB5", -->
<!--                       # "CPROB6", -->
<!--                       "CB", -->
<!--                       "CW", -->
<!--                       "MLCJOINT", -->
<!--                       "ID") -->

<!-- pp <- CW2CB2 %>%  -->
<!--   group_by(CW) %>%  -->
<!--   summarise(Breakfast_0 = sum(Breakfast == 0)/length(Breakfast),  -->
<!--             Breakfast_1 = sum(Breakfast == 1)/length(Breakfast),  -->
<!--             Breakfast_2 = sum(Breakfast == 2)/length(Breakfast), -->
<!--             Morning.snack_0 = sum(Morning.snack == 0)/length(Morning.snack), -->
<!--             Morning.snack_1 = sum(Morning.snack == 1)/length(Morning.snack),  -->
<!--             Morning.snack_2 = sum(Morning.snack == 2)/length(Morning.snack), -->
<!--             Lunch_0 = sum(Lunch == 0)/length(Lunch), -->
<!--             Lunch_1 = sum(Lunch == 1)/length(Lunch),  -->
<!--             Lunch_2 = sum(Lunch == 2)/length(Lunch), -->
<!--             Afternoon.snack_0 = sum(Afternoon.snack == 0)/length(Afternoon.snack), -->
<!--             Afternoon.snack_1 = sum(Afternoon.snack == 1)/length(Afternoon.snack),  -->
<!--             Afternoon.snack_2 = sum(Afternoon.snack == 2)/length(Afternoon.snack), -->
<!--             Dinner_0 = sum(Dinner == 0)/length(Dinner), -->
<!--             Dinner_1 = sum(Dinner == 1)/length(Dinner),  -->
<!--             Dinner_2 = sum(Dinner == 2)/length(Dinner), -->
<!--             Before.bedtime.snack_0 = sum(Before.bedtime.snack == 0)/length(Before.bedtime.snack), -->
<!--             Before.bedtime.snack_1 = sum(Before.bedtime.snack == 1)/length(Before.bedtime.snack),  -->
<!--             Before.bedtime.snack_2 = sum(Before.bedtime.snack == 2)/length(Before.bedtime.snack), -->
<!--             Midnight.food_0 = sum(Midnight.food == 0)/length(Midnight.food), -->
<!--             Midnight.food_1 = sum(Midnight.food == 1)/length(Midnight.food),  -->
<!--             Midnight.food_2 = sum(Midnight.food == 2)/length(Midnight.food)) -->



<!-- pp_long <- pp %>%  -->
<!--   gather(Hour, Prob, -CW) %>%  -->
<!--   separate(Hour, into = c("Slots", "Carbo"), sep = "_")  -->




<!-- pp_long$Slots <- factor(pp_long$Slots, levels = c("Breakfast",  -->
<!--                    "Morning.snack", -->
<!--                    "Lunch", -->
<!--                    "Afternoon.snack", -->
<!--                    "Dinner", -->
<!--                    "Before.bedtime.snack", -->
<!--                    "Midnight.food")) -->
<!-- ``` -->



<!-- ```{r echo=FALSE, fig.height=6, fig.width=14, message=FALSE, warning=FALSE, cache=TRUE} -->
<!-- library(ggthemr) -->
<!-- ggthemr("fresh", layout = "scientific") -->
<!-- library(ggplot2) -->

<!-- pp_long$Time <- as.character(pp_long$Slots) -->
<!-- pp_long$Time[pp_long$Slots == "Breakfast"] <- 7.5 -->
<!-- pp_long$Time[pp_long$Slots == "Morning.snack"] <- 10.5 -->
<!-- pp_long$Time[pp_long$Slots == "Lunch"] <- 13 -->
<!-- pp_long$Time[pp_long$Slots == "Afternoon.snack"] <- 15.5 -->
<!-- pp_long$Time[pp_long$Slots == "Dinner"] <- 18.5 -->
<!-- pp_long$Time[pp_long$Slots == "Before.bedtime.snack"] <- 21 -->
<!-- pp_long$Time[pp_long$Slots == "Midnight.food"] <- 26 -->
<!-- pp_long$Time <- as.numeric(pp_long$Time) -->


<!-- ggplot(pp_long[pp_long$CW == 1, ], aes(y = Prob, x=Time, group = Carbo, color = Carbo))  +  -->
<!--   scale_x_continuous(limits = c(6, 29), -->
<!--   breaks = seq(6, 29, by = 1)) + -->
<!--   annotate("rect", xmin = 6, xmax = 9, ymin = 0, ymax = 1.00,  -->
<!--             alpha = 0.5, fill = "grey") +  -->
<!--   annotate("rect", xmin = 12, xmax = 14, ymin = 0, ymax = 1.00,  -->
<!--              alpha = 0.5, fill = "grey") +  -->
<!--   annotate("rect", xmin = 17, xmax = 20, ymin = 0, ymax = 1.00,  -->
<!--             alpha = 0.5, fill = "grey") +  -->
<!--   annotate("rect", xmin = 22, xmax = 29, ymin = 0, ymax = 1.00,  -->
<!--              alpha = 0.5, fill = "grey") + -->
<!--   geom_point(size = 3) +  -->
<!--   geom_line(size = 1.5) +  -->
<!--   theme(axis.title = element_text(size = 18),  -->
<!--         axis.text = element_text(size = 18),  -->
<!--         axis.line = element_line(colour = "black"),  -->
<!--         panel.border = element_blank(),  -->
<!--         panel.background = element_blank(),  -->
<!--         legend.text = element_text(size = 15),  -->
<!--         legend.title = element_text(size = 15)  -->
<!--         # legend.position = "bottom",  -->
<!--         # legend.direction = "horizontal" -->
<!--   ) +  -->
<!--     # theme(axis.text.x = element_text(angle = 60, hjust = 1)) +  -->
<!--   labs(title = "Class 1 days", x = "Hours of the day (next day from hour 24)", y = "Probability", -->
<!--        color = "Carbohydrate\nintake") +  -->
<!--   scale_color_discrete(labels = c("Not eating", "< 50%", ">= 50%")) +  -->
<!--   ylim(c(0,1)) #+  -->
<!--   # scale_x_discrete(labels = c("6","7","8","9","10","11","12","13","14", -->
<!--   #                             "15","16","17","18","19", "20","21","22", -->
<!--   #                             "23","0","1","2","3","4","5")) -->


<!-- ggplot(pp_long[pp_long$CW == 2, ], aes(y = Prob, x=Time, group = Carbo, color = Carbo)) +  -->
<!--   scale_x_continuous(limits = c(6, 29), -->
<!--   breaks = seq(6, 29, by = 1)) + -->
<!--   annotate("rect", xmin = 6, xmax = 9, ymin = 0, ymax = 1.00,  -->
<!--             alpha = 0.5, fill = "grey") +  -->
<!--   annotate("rect", xmin = 12, xmax = 14, ymin = 0, ymax = 1.00,  -->
<!--              alpha = 0.5, fill = "grey") +  -->
<!--   annotate("rect", xmin = 17, xmax = 20, ymin = 0, ymax = 1.00,  -->
<!--             alpha = 0.5, fill = "grey") +  -->
<!--   annotate("rect", xmin = 22, xmax = 29, ymin = 0, ymax = 1.00,  -->
<!--              alpha = 0.5, fill = "grey") + -->
<!--   geom_point(size = 3) +  -->
<!--   geom_line(size = 1.5) +  -->
<!--   theme(axis.title = element_text(size = 18),  -->
<!--         axis.text = element_text(size = 18),  -->
<!--         axis.line = element_line(colour = "black"),  -->
<!--         panel.border = element_blank(),  -->
<!--         panel.background = element_blank(),  -->
<!--         legend.text = element_text(size = 15),  -->
<!--         legend.title = element_text(size = 15)  -->
<!--         # legend.position = "bottom",  -->
<!--         # legend.direction = "horizontal" -->
<!--   ) +  -->
<!--     # theme(axis.text.x = element_text(angle = 60, hjust = 1)) +  -->
<!--   labs(title = "Class 2 days", x = "Hours of the day (next day from hour 24)", y = "Probability", -->
<!--        color = "Carbohydrate\nintake") +  -->
<!--   scale_color_discrete(labels = c("Not eating", "< 50%", ">= 50%")) +  -->
<!--   ylim(c(0,1)) -->


<!-- ``` -->


<!-- ## Visualisation of level 2 latent classes (CB = 2) -->




<!-- ```{r echo=FALSE, fig.height=6, fig.width=7, message=FALSE, warning=FALSE, cache=TRUE} -->

<!-- # ndnsNNN <- read_csv("results/ndnsNNN.dat") -->
<!-- # dt <- ndnsNNN[, c(2,5)] -->
<!-- # names(dt) <- c("ID_DAY", "DayofWeek") -->
<!-- #  -->
<!-- #  -->
<!-- # CW2CB2 <- CW2CB2 %>%  -->
<!-- #   left_join(dt, by = "ID_DAY") -->
<!-- #  -->

<!-- chart.data <- CW2CB2 %>%  -->
<!--   group_by(CB, CW) %>%  -->
<!--   tally %>%  -->
<!--   group_by(CB) %>%  -->
<!--   mutate(pct = n/sum(n)) -->

<!-- chart.data <- ddply(chart.data, .(CB), -->
<!--                      transform, pos = cumsum(pct) - (0.5 * pct)) -->

<!-- chart.data$CW <- factor(chart.data$CW, levels = c("2", "1"),  -->
<!--                         labels = c("Class 2 days", "Class 1 days")) -->
<!-- chart.data$CB <- factor(chart.data$CB, levels = c("1", "2"),  -->
<!--                         labels = c("Individual Class 1\n(56.3%)",  "Individual class 2\n(43.7%)")) -->



<!-- library(ggthemr) -->
<!-- ggthemr("dust", layout = "scientific") -->
<!-- ggplot() +  -->
<!--   geom_bar(aes(y = pct, x = CB, fill = CW), data = chart.data, width = 0.6, -->
<!--            stat="identity") +  -->
<!--   geom_text(data=chart.data, aes(x = CB, y = pos, label = paste0(sprintf("%1.1f", pct*100),"%")), -->
<!--             size=4, colour="white", family="Atlas Grotesk Medium") +  -->
<!--   theme(legend.position="bottom", legend.direction="horizontal", -->
<!--         legend.title = element_blank(),  -->
<!--         axis.title = element_text(size = 18),  -->
<!--         axis.text = element_text(size = 15),  -->
<!--         axis.line = element_line(colour = "black"),  -->
<!--         plot.title=element_text(family="Atlas Grotesk Medium"), -->
<!--         text=element_text(family="Atlas Grotesk Light")) +  -->
<!--   labs(title = "Multilevel latent class solution", x = "Between Individual classes", y = "Percentage") + -->
<!--   scale_y_continuous(labels=percent) -->
<!-- ``` -->



<!-- ## Visualisation of level 2 latent classes (CB = 3) -->


<!-- ```{r echo=FALSE, fig.height=6, fig.width=7, message=FALSE, warning=FALSE, cache=TRUE} -->


<!-- CW2CB3 <- read_table2("/home/wangcc-me/Documents/LSHTMproject/results/Timeslots/NDNSslot_CW2CB3.txt", -->
<!--                          col_names = FALSE) -->

<!-- names(CW2CB3) <- c("Breakfast",  -->
<!--                    "Morning.snack", -->
<!--                    "Lunch", -->
<!--                    "Afternoon.snack", -->
<!--                    "Dinner", -->
<!--                    "Before.bedtime.snack", -->
<!--                    "Midnight.food", -->
<!--                       "ID_DAY", -->
<!--                       "AGE", -->
<!--                       "SEX", -->
<!--                       "CPROB1", -->
<!--                       "CPROB2", -->
<!--                       "CPROB3", -->
<!--                       "CPROB4", -->
<!--                       "CPROB5", -->
<!--                       "CPROB6", -->
<!--                       "CB", -->
<!--                       "CW", -->
<!--                       "MLCJOINT", -->
<!--                       "ID") -->




<!-- chart.data <- CW2CB3 %>%  -->
<!--   group_by(CB, CW) %>%  -->
<!--   tally %>%  -->
<!--   group_by(CB) %>%  -->
<!--   mutate(pct = n/sum(n)) -->


<!-- # chart.data$CW[chart.data$CW == 1] <- 0  -->
<!-- # chart.data$CW[chart.data$CW == 3] <- 1  -->
<!-- # chart.data$CW[chart.data$CW == 0] <- 3  -->

<!-- chart.data <- chart.data[order(chart.data$CB, chart.data$CW),] -->
<!-- chart.data <- ddply(chart.data, .(CB),  -->
<!--                     transform, pos = cumsum(pct) - (0.5 * pct))  -->



<!-- chart.data$CW <- factor(chart.data$CW, levels = c("2", "1"),  -->
<!--                         labels = c("Class 2 days", "Class 1 days")) -->
<!-- chart.data$CB <- factor(chart.data$CB, levels = c("1", "2", "3"),  -->
<!--                         labels = c("Individual\nclass 1\n(42.4%)",  "Individual\nclass 2\n(29.5%)",  -->
<!--                                    "Individual\nclass 3\n(28.1%)")) -->



<!-- library(ggthemr) -->
<!-- ggthemr("dust", layout = "scientific") -->
<!-- ggplot() +  -->
<!--   geom_bar(aes(y = pct, x = CB, fill = CW), data = chart.data, width = 0.6, -->
<!--            stat="identity") +  -->
<!--   geom_text(data=chart.data, aes(x = CB, y = pos, label = paste0(sprintf("%1.1f", pct*100),"%")), -->
<!--             size=4, colour="white", family="Atlas Grotesk Medium") +  -->
<!--   theme(legend.position="bottom", legend.direction="horizontal", -->
<!--         legend.title = element_blank(),  -->
<!--         axis.title = element_text(size = 18),  -->
<!--         axis.text = element_text(size = 15),  -->
<!--         axis.line = element_line(colour = "black"),  -->
<!--         plot.title=element_text(family="Atlas Grotesk Medium"), -->
<!--         text=element_text(family="Atlas Grotesk Light")) +  -->
<!--   labs(title = "Multilevel latent class solution", x = "Between Individual classes", y = "Percentage") + -->
<!--   scale_y_continuous(labels=percent) -->
<!-- ``` -->


<!-- ## Visualisation of level 2 latent classes (CB = 4) -->


<!-- ```{r echo=FALSE, fig.height=6, fig.width=7, message=FALSE, warning=FALSE, cache=TRUE} -->


<!-- CW2CB4 <- read_table2("/home/wangcc-me/Documents/LSHTMproject/results/Timeslots/NDNSslot_CW2CB4.txt", -->
<!--                          col_names = FALSE) -->

<!-- names(CW2CB4) <- c("Breakfast",  -->
<!--                    "Morning.snack", -->
<!--                    "Lunch", -->
<!--                    "Afternoon.snack", -->
<!--                    "Dinner", -->
<!--                    "Before.bedtime.snack", -->
<!--                    "Midnight.food", -->
<!--                       "ID_DAY", -->
<!--                       "AGE", -->
<!--                       "SEX", -->
<!--                       "CPROB1", -->
<!--                       "CPROB2", -->
<!--                       "CPROB3", -->
<!--                       "CPROB4", -->
<!--                       "CPROB5", -->
<!--                       "CPROB6", -->
<!--                       "CPROB7", -->
<!--                       "CPROB8", -->
<!--                       "CB", -->
<!--                       "CW", -->
<!--                       "MLCJOINT", -->
<!--                       "ID") -->




<!-- chart.data <- CW2CB4 %>%  -->
<!--   group_by(CB, CW) %>%  -->
<!--   tally %>%  -->
<!--   group_by(CB) %>%  -->
<!--   mutate(pct = n/sum(n)) -->


<!-- # chart.data$CW[chart.data$CW == 1] <- 0  -->
<!-- # chart.data$CW[chart.data$CW == 3] <- 1  -->
<!-- # chart.data$CW[chart.data$CW == 0] <- 3  -->

<!-- chart.data <- chart.data[order(chart.data$CB, chart.data$CW),] -->
<!-- chart.data <- ddply(chart.data, .(CB),  -->
<!--                     transform, pos = cumsum(pct) - (0.5 * pct))  -->



<!-- chart.data$CW <- factor(chart.data$CW, levels = c("2", "1"),  -->
<!--                         labels = c("Class 2 days", "Class 1 days")) -->
<!-- chart.data$CB <- factor(chart.data$CB, levels = c("1", "2", "3", "4"),  -->
<!--                         labels = c("Individual\nclass 1\n(23.4%)",  "Individual\nclass 2\n(23.7%)",  -->
<!--                                    "Individual\nclass 3\n(28.9%)", "Individual\nclass 4\n(23.9%)")) -->



<!-- library(ggthemr) -->
<!-- ggthemr("dust", layout = "scientific") -->
<!-- ggplot() +  -->
<!--   geom_bar(aes(y = pct, x = CB, fill = CW), data = chart.data, width = 0.6, -->
<!--            stat="identity") +  -->
<!--   geom_text(data=chart.data, aes(x = CB, y = pos, label = paste0(sprintf("%1.1f", pct*100),"%")), -->
<!--             size=4, colour="white", family="Atlas Grotesk Medium") +  -->
<!--   theme(legend.position="bottom", legend.direction="horizontal", -->
<!--         legend.title = element_blank(),  -->
<!--         axis.title = element_text(size = 18),  -->
<!--         axis.text = element_text(size = 15),  -->
<!--         axis.line = element_line(colour = "black"),  -->
<!--         plot.title=element_text(family="Atlas Grotesk Medium"), -->
<!--         text=element_text(family="Atlas Grotesk Light")) +  -->
<!--   labs(title = "Multilevel latent class solution", x = "Between Individual classes", y = "Percentage") + -->
<!--   scale_y_continuous(labels=percent) -->
<!-- ``` -->



# (CW = 3) Level 1 latent classes 

## Visualisation of level 1 latent classes 

```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

CW3CB2 <- read_table2("/home/wangcc-me/Documents/LSHTMproject/results/Timeslots/NDNSslot_CW3CB2.txt",
                         col_names = FALSE)

names(CW3CB2) <- c("Breakfast", 
                   "Morning.snack",
                   "Lunch",
                   "Afternoon.snack",
                   "Dinner",
                   "Before.bedtime.snack",
                   "Midnight.food",
                      "ID_DAY",
                      "AGE",
                      "SEX",
                      "CPROB1",
                      "CPROB2",
                      "CPROB3",
                      "CPROB4",
                      "CPROB5",
                      "CPROB6",
                      # "CPROB7",
                      # "CPROB8",
                      # "CPROB9",
                      "CB",
                      "CW",
                      "MLCJOINT",
                      "ID")

pp <- CW3CB2 %>% 
  group_by(CW) %>% 
  summarise(Breakfast_0 = sum(Breakfast == 0)/length(Breakfast), 
            Breakfast_1 = sum(Breakfast == 1)/length(Breakfast), 
            Breakfast_2 = sum(Breakfast == 2)/length(Breakfast),
            Morning.snack_0 = sum(Morning.snack == 0)/length(Morning.snack),
            Morning.snack_1 = sum(Morning.snack == 1)/length(Morning.snack), 
            Morning.snack_2 = sum(Morning.snack == 2)/length(Morning.snack),
            Lunch_0 = sum(Lunch == 0)/length(Lunch),
            Lunch_1 = sum(Lunch == 1)/length(Lunch), 
            Lunch_2 = sum(Lunch == 2)/length(Lunch),
            Afternoon.snack_0 = sum(Afternoon.snack == 0)/length(Afternoon.snack),
            Afternoon.snack_1 = sum(Afternoon.snack == 1)/length(Afternoon.snack), 
            Afternoon.snack_2 = sum(Afternoon.snack == 2)/length(Afternoon.snack),
            Dinner_0 = sum(Dinner == 0)/length(Dinner),
            Dinner_1 = sum(Dinner == 1)/length(Dinner), 
            Dinner_2 = sum(Dinner == 2)/length(Dinner),
            Before.bedtime.snack_0 = sum(Before.bedtime.snack == 0)/length(Before.bedtime.snack),
            Before.bedtime.snack_1 = sum(Before.bedtime.snack == 1)/length(Before.bedtime.snack), 
            Before.bedtime.snack_2 = sum(Before.bedtime.snack == 2)/length(Before.bedtime.snack),
            Midnight.food_0 = sum(Midnight.food == 0)/length(Midnight.food),
            Midnight.food_1 = sum(Midnight.food == 1)/length(Midnight.food), 
            Midnight.food_2 = sum(Midnight.food == 2)/length(Midnight.food))



pp_long <- pp %>% 
  gather(Hour, Prob, -CW) %>% 
  separate(Hour, into = c("Slots", "Carbo"), sep = "_") 




pp_long$Slots <- factor(pp_long$Slots, levels = c("Breakfast", 
                   "Morning.snack",
                   "Lunch",
                   "Afternoon.snack",
                   "Dinner",
                   "Before.bedtime.snack",
                   "Midnight.food"))
```



```{r echo=FALSE,fig.height=6, fig.width=14, message=FALSE, warning=FALSE, cache=TRUE}
library(ggthemr)
ggthemr("fresh", layout = "scientific")
library(ggplot2)


pp_long$Time <- as.character(pp_long$Slots)
pp_long$Time[pp_long$Slots == "Breakfast"] <- 7.5
pp_long$Time[pp_long$Slots == "Morning.snack"] <- 10.5
pp_long$Time[pp_long$Slots == "Lunch"] <- 13
pp_long$Time[pp_long$Slots == "Afternoon.snack"] <- 15.5
pp_long$Time[pp_long$Slots == "Dinner"] <- 18.5
pp_long$Time[pp_long$Slots == "Before.bedtime.snack"] <- 21
pp_long$Time[pp_long$Slots == "Midnight.food"] <- 26
pp_long$Time <- as.numeric(pp_long$Time)


ggplot(pp_long[pp_long$CW == 1, ], aes(y = Prob, x=Time, group = Carbo, color = Carbo))  + 
  scale_x_continuous(limits = c(6, 29),
  breaks = seq(6, 29, by = 1)) +
  annotate("rect", xmin = 6, xmax = 9, ymin = 0, ymax = 1.00, 
            alpha = 0.5, fill = "grey") + 
  annotate("rect", xmin = 12, xmax = 14, ymin = 0, ymax = 1.00, 
             alpha = 0.5, fill = "grey") + 
  annotate("rect", xmin = 17, xmax = 20, ymin = 0, ymax = 1.00, 
            alpha = 0.5, fill = "grey") + 
  annotate("rect", xmin = 22, xmax = 29, ymin = 0, ymax = 1.00, 
             alpha = 0.5, fill = "grey") +
  geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
  ) + 
    # theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
  labs(title = "Class 1 days", x = "Hours of the day (next day from hour 24)", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Not eating", "< 50%", ">= 50%")) + 
  ylim(c(0,1)) #+ 
  # scale_x_discrete(labels = c("6","7","8","9","10","11","12","13","14",
  #                             "15","16","17","18","19", "20","21","22",
  #                             "23","0","1","2","3","4","5"))


ggplot(pp_long[pp_long$CW == 2, ], aes(y = Prob, x=Time, group = Carbo, color = Carbo)) + 
  scale_x_continuous(limits = c(6, 29),
  breaks = seq(6, 29, by = 1)) +
  annotate("rect", xmin = 6, xmax = 9, ymin = 0, ymax = 1.00, 
            alpha = 0.5, fill = "grey") + 
  annotate("rect", xmin = 12, xmax = 14, ymin = 0, ymax = 1.00, 
             alpha = 0.5, fill = "grey") + 
  annotate("rect", xmin = 17, xmax = 20, ymin = 0, ymax = 1.00, 
            alpha = 0.5, fill = "grey") + 
  annotate("rect", xmin = 22, xmax = 29, ymin = 0, ymax = 1.00, 
             alpha = 0.5, fill = "grey") +
  geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
  ) + 
    # theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
  labs(title = "Class 2 days", x = "Hours of the day (next day from hour 24)", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Not eating", "< 50%", ">= 50%")) + 
  ylim(c(0,1))

ggplot(pp_long[pp_long$CW == 3, ], aes(y = Prob, x=Time, group = Carbo, color = Carbo)) + 
  scale_x_continuous(limits = c(6, 29),
  breaks = seq(6, 29, by = 1)) +
  annotate("rect", xmin = 6, xmax = 9, ymin = 0, ymax = 1.00, 
            alpha = 0.5, fill = "grey") + 
  annotate("rect", xmin = 12, xmax = 14, ymin = 0, ymax = 1.00, 
             alpha = 0.5, fill = "grey") + 
  annotate("rect", xmin = 17, xmax = 20, ymin = 0, ymax = 1.00, 
            alpha = 0.5, fill = "grey") + 
  annotate("rect", xmin = 22, xmax = 29, ymin = 0, ymax = 1.00, 
             alpha = 0.5, fill = "grey") +
  geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
  ) + 
    # theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
  labs(title = "Class 3 days", x = "Hours of the day (next day from hour 24)", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Not eating", "< 50%", ">= 50%")) + 
  ylim(c(0,1))


```



## Visualisation of level 2 latent classes (CB = 2)




```{r echo=FALSE, fig.height=6, fig.width=7, message=FALSE, warning=FALSE, cache=TRUE}


CW3CB2 <- read_table2("/home/wangcc-me/Documents/LSHTMproject/results/Timeslots/NDNSslot_CW3CB2.txt",
                      col_names = FALSE)

names(CW3CB2) <- c("Breakfast", "Morning.snack", "Lunch",
                   "Afternoon.snack", "Dinner", "Before.bedtime.snack",
                   "Midnight.food", "ID_DAY", "AGE", "SEX",
                   "CPROB1", "CPROB2", "CPROB3", "CPROB4",
                   "CPROB5", "CPROB6",
                   # "CPROB7",
                   # "CPROB8",
                   # "CPROB9",
                   "CB", "CW", "MLCJOINT", "ID")


CW3CB3 <- read_table2("/home/wangcc-me/Documents/LSHTMproject/results/Timeslots/NDNSslot_CW3CB3.txt",
                      col_names = FALSE)

names(CW3CB3) <- c("Breakfast",  "Morning.snack", "Lunch",
                   "Afternoon.snack", "Dinner", "Before.bedtime.snack",
                   "Midnight.food", "ID_DAY", "AGE", "SEX",
                   "CPROB1", "CPROB2", "CPROB3", "CPROB4",
                   "CPROB5", "CPROB6", "CPROB7", "CPROB8",
                   "CPROB9", "CB", "CW", "MLCJOINT", "ID")

# tab1(CW3CB2$CW)
# tab1(CW3CB3$CW)

CW3CB3$CW_new <- 0
CW3CB3$CW_new[CW3CB3$CW == 1] <- 3
CW3CB3$CW_new[CW3CB3$CW == 2] <- 1
CW3CB3$CW_new[CW3CB3$CW == 3] <- 2

CB2_in_CW3CB2 <- CW3CB2 %>% 
  select(ID, ID_DAY, CW, CB) %>% 
  rename(CW3_in_2 = CW, CB2_in_2 = CB)
CW3CB3 <- CW3CB3 %>% 
  left_join(CB2_in_CW3CB2, by = "ID_DAY")


chart.data <- CW3CB3 %>%
  group_by(CB2_in_2, CW_new) %>%
  tally %>%
  group_by(CB2_in_2) %>%
  mutate(pct = n/sum(n))

chart.data <- chart.data[order(chart.data$CB2_in_2, chart.data$CW_new),]


chart.data <- ddply(chart.data, .(CB2_in_2),
                     transform, pos = cumsum(pct) - (0.5 * pct))

chart.data$CW_new <- factor(chart.data$CW_new, levels = c("3", "2", "1"),
                        labels = c("Regular\nmeals day", "low carbo-\nhydrate day", "High carbo-\nhydrate day"))
chart.data$CB2_in_2 <- factor(chart.data$CB2_in_2, levels = c("1", "2"),
                        labels = c("Individual Class 1\n(35.3%)",  "Individual class 2\n(64.7%)"))



library(ggthemr)
ggthemr("dust", layout = "scientific")
ggplot() +
  geom_bar(aes(y = pct, x = CB2_in_2, fill = CW_new), data = chart.data, width = 0.6,
           stat="identity") +
  geom_text(data=chart.data, aes(x = CB2_in_2, y = pos, label = paste0(sprintf("%1.1f", pct*100),"%")),
            size=4, colour="white", family="Atlas Grotesk Medium") +
  theme(legend.position="bottom", legend.direction="horizontal",
        legend.title = element_blank(),
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 15),
        axis.line = element_line(colour = "black"),
        plot.title=element_text(family="Atlas Grotesk Medium"),
        text=element_text(family="Atlas Grotesk Light")) +
  labs(title = "Multilevel latent class solution", x = "Between Individual classes", y = "Percentage") +
  scale_y_continuous(labels=percent)
```



## Visualisation of level 2 latent classes (CB = 3)


```{r echo=FALSE, fig.height=6, fig.width=7, message=FALSE, warning=FALSE, cache=TRUE}


CW3CB3 <- read_table2("/home/wangcc-me/Documents/LSHTMproject/results/Timeslots/NDNSslot_CW3CB3.txt",
                         col_names = FALSE)

names(CW3CB3) <- c("Breakfast", 
                   "Morning.snack",
                   "Lunch",
                   "Afternoon.snack",
                   "Dinner",
                   "Before.bedtime.snack",
                   "Midnight.food",
                      "ID_DAY",
                      "AGE",
                      "SEX",
                      "CPROB1",
                      "CPROB2",
                      "CPROB3",
                      "CPROB4",
                      "CPROB5",
                      "CPROB6",
                      "CPROB7",
                      "CPROB8",
                      "CPROB9",
                      "CB",
                      "CW",
                      "MLCJOINT",
                      "ID")




chart.data <- CW3CB3 %>% 
  group_by(CB, CW) %>% 
  tally %>% 
  group_by(CB) %>% 
  mutate(pct = n/sum(n))


chart.data$CW_new <- 0
chart.data$CW_new[chart.data$CW == 1] <- 3
chart.data$CW_new[chart.data$CW == 2] <- 1
chart.data$CW_new[chart.data$CW == 3] <- 2


chart.data <- chart.data[order(chart.data$CB, chart.data$CW_new),]
chart.data <- ddply(chart.data, .(CB), 
                    transform, pos = cumsum(pct) - (0.5 * pct)) 



chart.data$CW_new <- factor(chart.data$CW_new, levels = c("3", "2", "1"), 
                        labels = c("Regular\nmeals day", "low carbo-\nhydrate day", "High carbo-\nhydrate day"))
chart.data$CB <- factor(chart.data$CB, levels = c("1", "2", "3"), 
                        labels = c("Individual\nclass 1\n(28.0%)",  "Individual\nclass 2\n(28.6%)", "Individual\nclass 3\n(43.4%)"))



library(ggthemr)
ggthemr("dust", layout = "scientific")
ggplot() + 
  geom_bar(aes(y = pct, x = CB, fill = CW_new), data = chart.data, width = 0.6,
           stat="identity") + 
  geom_text(data=chart.data, aes(x = CB, y = pos, label = paste0(sprintf("%1.1f", pct*100),"%")),
            size=4, colour="white", family="Atlas Grotesk Medium") + 
  theme(legend.position="bottom", legend.direction="horizontal",
        legend.title = element_blank(), 
        axis.title = element_text(size = 18), 
        axis.text = element_text(size = 15), 
        axis.line = element_line(colour = "black"), 
        plot.title=element_text(family="Atlas Grotesk Medium"),
        text=element_text(family="Atlas Grotesk Light")) + 
  labs(title = "Multilevel latent class solution", x = "Between Individual classes", y = "Percentage") +
  scale_y_continuous(labels=percent)
```


## Visualisation of level 2 latent classes (CB = 4)


```{r echo=FALSE, fig.height=6, fig.width=7, message=FALSE, warning=FALSE, cache=TRUE}


CW3CB4 <- read_table2("/home/wangcc-me/Documents/LSHTMproject/results/Timeslots/NDNSslot_CW3CB4.txt",
                         col_names = FALSE)

names(CW3CB4) <- c("Breakfast", 
                   "Morning.snack",
                   "Lunch",
                   "Afternoon.snack",
                   "Dinner",
                   "Before.bedtime.snack",
                   "Midnight.food",
                      "ID_DAY",
                      "AGE",
                      "SEX",
                      "CPROB1",
                      "CPROB2",
                      "CPROB3",
                      "CPROB4",
                      "CPROB5",
                      "CPROB6",
                      "CPROB7",
                      "CPROB8",
                      "CPROB9",
                      "CPROB10",
                      "CPROB11",
                      "CPROB12",
                      "CB",
                      "CW",
                      "MLCJOINT",
                      "ID")




chart.data <- CW3CB4 %>% 
  group_by(CB, CW) %>% 
  tally %>% 
  group_by(CB) %>% 
  mutate(pct = n/sum(n))


chart.data$CW_new <- 0
chart.data$CW_new[chart.data$CW == 1] <- 3
chart.data$CW_new[chart.data$CW == 2] <- 1
chart.data$CW_new[chart.data$CW == 3] <- 2


chart.data <- chart.data[order(chart.data$CB, chart.data$CW_new),]
chart.data <- ddply(chart.data, .(CB), 
                    transform, pos = cumsum(pct) - (0.5 * pct)) 



chart.data$CW_new <- factor(chart.data$CW_new, levels = c("3", "2", "1"), 
                        labels = c("Class 3 days", "Class 2 days", "Class 1 days"))
chart.data$CB <- factor(chart.data$CB, levels = c("1", "2", "3", "4"), 
                        labels = c("Individual\nclass 1\n(21.8%)",  "Individual\nclass 2\n(21.1%)", 
                                   "Individual\nclass 3\n(33.8%)", "Individual\nclass 4\n(23.3%)"))



library(ggthemr)
ggthemr("dust", layout = "scientific")
ggplot() + 
  geom_bar(aes(y = pct, x = CB, fill = CW_new), data = chart.data, width = 0.6,
           stat="identity") + 
  geom_text(data=chart.data, aes(x = CB, y = pos, label = paste0(sprintf("%1.1f", pct*100),"%")),
            size=4, colour="white", family="Atlas Grotesk Medium") + 
  theme(legend.position="bottom", legend.direction="horizontal",
        legend.title = element_blank(), 
        axis.title = element_text(size = 18), 
        axis.text = element_text(size = 15), 
        axis.line = element_line(colour = "black"), 
        plot.title=element_text(family="Atlas Grotesk Medium"),
        text=element_text(family="Atlas Grotesk Light")) + 
  labs(title = "Multilevel latent class solution", x = "Between Individual classes", y = "Percentage") +
  scale_y_continuous(labels=percent)
```

